QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-3.tex
update number of total and quad conss in text

Similarly, Figure~\ref{fig:pic_constr} (left)
%Figure~\ref{fig:pic_constr_medium}
%and Figure~\ref{fig:pic_constr_big}
describes how the number of linear and quadratic
constraints are distributed within the instances. The instances are sorted
accordingly to the total number of constraints.
% and divided in the same manner as for Figures~\ref{fig:pic_var_small}--\ref{fig:pic_var_large}.
For each instance we report the total number of constraints with a ``$+$''
and the total number of quadratic constraints
with a ``$\times$''. Also, in this case, different percentages of linear and
quadratic constraints are present and well-distributed across the spectrum
of constraint sizes, although both medium- and large-size instances show a
prevalence of lower percentages of quadratic constraints. In particular,
from Figure~\ref{fig:pic_constr} (left) we learn that while the maximum number
of linear constraints exceeds 100000, the maximum number of quadratic
constraints tops up at around 10000. This is, however, reasonable, considering
how quadratic constraints can, in general, be expected to be much more
computationally challenging than linear ones, especially if nonconvex.

>>>>

Similarly, Figure~\ref{fig:pic_constr} (left)
%Figure~\ref{fig:pic_constr_medium}
%and Figure~\ref{fig:pic_constr_big}
describes how the number of linear and quadratic
constraints are distributed within the instances. The instances are sorted
accordingly to the total number of constraints.
% and divided in the same manner as for Figures~\ref{fig:pic_var_small}--\ref{fig:pic_var_large}.
For each instance we report the total number of constraints with a ``$+$''
and the total number of quadratic constraints
with a ``$\times$''. Also in this case, different percentages of linear and
quadratic constraints are present and well-distributed across the spectrum
of constraint sizes, although both medium- and large-size instances show a
prevalence of lower percentages of quadratic constraints. In particular,
from Figure~\ref{fig:pic_constr} (left) we learn that while the maximum number
of linear constraints exceeds 1,000,000, the maximum number of quadratic
constraints tops up at 140,000. This is, however, reasonable, considering
how quadratic constraints can, in general, be expected to be much more
computationally challenging than linear ones, especially if nonconvex.
